Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-11-30 paper/reply.tex
add [Experimental evaluation, #1/#2/#3]

\noindent \textbf{[Novelty, \#1/\#2]}

@@

@@

3) I believe equation (10) does not correspond to the system on Figure 1. Please check. If needed, correct (11), (12) and (13) and the rest of the paper accordingly.
\begin{quote}
\textcolor{blue}{\textbf{Response:}
In fact, these equations are wrong. They have to be substituted by the following equations (1)-(5). This mistake does not affect the results and conclusions because the proposition 1 is still valid for this set of equations.
%%
%\begin{equation}
%\hat{Y}(z)=\nu_{1}(z)+Y(z)
%\end{equation}
%%
%\begin{equation}
%Y(z)=\hat{G}(z)\cdot(U(z)+\nu_{2}(z))
%\end{equation}
%%
%\begin{equation}
%U(z)=C(z)\cdot e(z)=C(z)\cdot (R(z)-\hat{Y}(z))
%\end{equation}
%%
%$$
%\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot [\hat{C}(z)\cdot(R(z)-\hat{Y}(z))+\nu_{2}(z)]
%$$
%%
\begin{equation}
\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z)
\end{equation}
%
\begin{equation}
\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z)
\end{equation}
%
\begin{equation}
H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
\begin{equation}
H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
\begin{equation}
H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Dario).
The benchmarks used are from existing work on verification. There are no FWL synthesis papers that we are aware of that we can compare with (known synthesis tools do not account for the FWL effects), so we make the comparison between the direct (SAT) and CEGIS approach on known benchmarks which is as close as we can get to these comparisons. 
}
\end{quote}

>>>>

\noindent \textbf{[Novelty, \#1/\#2/\#3]}

\noindent  As far as we know, the present synthesis approach that addresses FWL uncertainties in digital controllers has not been described or evaluated in the literature.
This work is the first to address FWL uncertainties based on CEGIS in the digital controller synthesis phase.

@@

\noindent \textbf{[Experimental evaluation, \#1/\#2/\#3]}

\noindent We have evaluated our approach using standard benchmarks taken mostly from the classical control literature [3,15,21,22,35]. Note that the used benchmarks are typically from existing work on control system verification. Larger benchmarks would strengthen our claims; however, related work on controller verification typically considers even smaller benchmarks (cf. 3.5 and 4.1).  Additionally, we only state the winning back-end in the results table, annotating where the one-stage engine was faster. The two order of magnitudes were measured empirically, since the one-stage engine times out on the majority of benchmarks.

@@

3) I believe equation (10) does not correspond to the system on Figure 1. Please check. If needed, correct (11), (12) and (13) and the rest of the paper accordingly.
\begin{quote}
\textcolor{blue}{\textbf{Response:}
In fact, these equations are wrong. They have to be substituted by the following equations (1)-(5). This mistake does not affect the results and conclusions because the proposition 1 is still valid for this set of equations.
%%
\begin{equation}
\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z)
\end{equation}
%
\begin{equation}
\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z)
\end{equation}
%
\begin{equation}
H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
\begin{equation}
H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
\begin{equation}
H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} The benchmarks used are from existing work on verification. There are no FWL synthesis papers that we are aware of that we can compare with (known synthesis tools do not account for the FWL effects), so we make the comparison between the direct (SAT) and CEGIS approach on known benchmarks which is as close as we can get to these comparisons. }
\end{quote}
